%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}

\cventry
{Research Assistant} % Job title
{University of Calgary} % Organization
{Calgary, Canada} % Location
{September 2021 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working on accelerating and monitoring network performance of different distributed systems such as distributed machine learning platforms, spark, storage engines, etc.}
\begin{itemize}
    \item Extracted system traces when a specific workload is running on the network
    \item Extracted time-series from the traces and perform future forecasting on the time-series
    \item Xgboost and PyTorch are used for forecasting
    \item Examined workloads are Spark, Distributed Deep Learning Training, etc.
    \item Using eBPF to extract low-level system traces
\end{itemize}
\end{cvitems}
}
%------------------------------------------------    
\cventry
{Team Leader} % Job title
{\href{https://cafebazaar.ir}{CafeBazaar}} % Organization
{Tehran, Iran} % Location
{September 2020 - August 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Leading real estate vertical team of \href{https://divar.ir}{Divar}. a team of 17 people, Consisting of different professions such as software engineers, data scientists, and UX designers.}
\item {1st Real Estate vertical classified product of iran in case of active users, total requests, ads count.}
\item {Responsible for deciding on technical problems, technical quality, team delivery, and members' growth.}
\end{cvitems}
}
%------------------------------------------------
\cventry
{Software Engineer} % Job title
{\href{https://cafebazaar.ir}{CafeBazaar}} % Organization
{Tehran, Iran} % Location
{October 2018 - August 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Software Engineer at infra team in Divar (a part of CafeBazaar group), the leading classified advertisement platform and the most popular app in Iran with more than 20 million users on all platforms.}
\item {Designer and system owner of ad search and submission stack. Streamlined the whole process, so Divar can handle more requests from users. Designed different features in submit forms to reach a compelling UX experience for users.}
\begin{itemize}
    \item Worked extensively on systems written in Python and Go.
    \item Worked with data systems such as Elasticsearch and Postgresql.
    \item Used Kubernetes as orchestration system, for deployment of microservices, API gateways and some of our databases (such as MongoDB or Redis)
    \item Managing CI/CD pipelines of these projects for ease of development for other team members.
\end{itemize}
\item {Responsible for interviewing new software engineer candidates and improvement of the technical interview process.}
\end{cvitems} 
}
%------------------------------------------------
\cventry
{Intern} % Job title
{\href{https://cafebazaar.ir}{CafeBazaar}} % Organization
{Tehran, Iran} % Location
{June 2018 - August 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {On-site summer internship.}
\item {Learned SRE and advanced software development concepts.}
\end{cvitems} 
}
%------------------------------------------------
\cventry
{Software Engineer} % Job title
{Erixe} % Organization
{Tehran, Iran} % Location
{February 2016 - June 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Software Engineer in \href{https://cafebazaar.ir/app/com.laklakian.android?l=en}{LakLak} team (a social network for pregnant woman)}.
\item {Responsible for frondend and backend of \href{https://cafebazaar.ir/app/com.laklakian.android?l=en}{LakLak}.}
\begin{itemize}
    \item Worked on the backend code which was on NodeJs and Frontend.
\end{itemize}
\end{cvitems} 
}
%------------------------------------------------

\end{cventries}
